MLH1 Results Outline

### 2020-02-10 doc/Results.rmd
work on 1CO landscape section

#### Predictions

@@

```{r Q1.Nrm.F1pos, echo=FALSE}

#calq the means for normalized F1

@@

```{r MM_CO_pos, echo=FALSE, eval=FALSE}
#use the 1CO
#Use MELT DF
#MELT_Curated_BivData

@@

```{r log.reg.CO1_pos, echo=FALSE, eval=FALSE}

@@

```{r t.test_1CO_pos, echo=FALSE, eval=FALSE}

@@

#### Nrm_1COpos_HetC_M3

>>>>

@@

```{r Q1.Nrm.F1pos_M2, echo=FALSE}

#calq the means for normalized F1
#M2

Q1.glm_nrmF1pos_M2 <- glm(norm.first.foci.pos ~ strain * sex, data=Mouse.Table_BivData_4MM)
#summary(Q1.glm_nrmF1pos_M2)

#DOM
Q1.glm_nrmF1pos_M2_Dom <- glm(norm.first.foci.pos ~ strain * sex, data=Mouse.Table_BivData_4MM[Mouse.Table_BivData_4MM$subsp == "Dom",])
#summary(Q1.glm_nrmF1pos_M2_Dom)

#MUSC
Q1.glm_nrmF1pos_M2_Musc <- glm(norm.first.foci.pos ~ strain * sex, data=Mouse.Table_BivData_4MM[Mouse.Table_BivData_4MM$subsp == "Musc",])
#summary(Q1.glm_nrmF1pos_M2_Musc)

#MOL
Q1.glm_nrmF1pos_M2_Mol <- glm(norm.first.foci.pos ~ strain * sex, data=Mouse.Table_BivData_4MM[Mouse.Table_BivData_4MM$subsp == "Mol",])
#summary(Q1.glm_nrmF1pos_M2_Mol)

```{r Q1.Nrm.F1pos_M2_long.biv, echo=FALSE}

#table for the 1CO long biv across strain and sexes?

@@

```{r Q1.MM_CO_pos, echo=FALSE, eval=FALSE}
#use the 1CO
#Use MELT DF
#MELT_Curated_BivData

@@

```{r Q1.nrmFoci1_M1, echo=FALSE}

#M1

```{r Q1.log.reg.CO1_pos, echo=FALSE, eval=FALSE}

@@

```{r Q1.t.test_1CO_pos, echo=FALSE, eval=FALSE}

@@
